Political Support in the United States

### 2024-03-12 paper/paper.qmd
Update paper.qmd

---
title: "Datasheet for 'A dataset'"
author: 
  - Yang Zhou
  - Yuean Wang
  - Dong Jun Yoon
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
date: today
date-format: long
abstract: "There is no other nation in the world that conducts elections the way the United States does. Local government representatives oversee elections in around 8,000 distinct jurisdictions. They are then under the general supervision of authorities, who are frequently selected through election procedures or partisan appointees. Typically, the voter liaison at the polling place is a temporary worker who works unpaid for a single day and only gets a few hours of training. These distinctive characteristics of our electoral system, along with the fact that Americans vote more frequently than citizens in other countries on a wider range of issues and positions, create special difficulties for the efficient administration of elections that voters across demand and deserve.
None of the other nations' electoral systems display all or any of these traits, but none have the same mix of US administrative traits. The quality of administration differs from jurisdiction to jurisdiction and even from polling place to polling place because of decentralization and dependence on volunteers. Because partisan officials will be involved, accusations of partisanship regarding the rules or their interpretation may arise based on the outcome of the judgments made by the officials and who stands to gain from it. The quantity and variety of democratic options in protracted elections have outpaced voters' attention spans and cognitive capacities. These distinguishing characteristics of our voting system contribute to the issues seen in the most recent elections. This paper is mainly based on the 2022 US election."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Political Support in the United States'"
author: 
  - Dong Jun Yoon
  - Yuean Wang
  - Yang Zhou
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
date: today
date-format: long
abstract: "There is no other nation in the world that conducts elections the way the United States does. Local government representatives oversee elections in around 8,000 distinct jurisdictions. They are then under the general supervision of authorities, who are frequently selected through election procedures or partisan appointees. Typically, the voter liaison at the polling place is a temporary worker who works unpaid for a single day and only gets a few hours of training. These distinctive characteristics of our electoral system, along with the fact that Americans vote more frequently than citizens in other countries on a wider range of issues and positions, create special difficulties for the efficient administration of elections that voters across demand and deserve.
None of the other nations' electoral systems display all or any of these traits, but none have the same mix of US administrative traits. The quality of administration differs from jurisdiction to jurisdiction and even from polling place to polling place because of decentralization and dependence on volunteers. Because partisan officials will be involved, accusations of partisanship regarding the rules or their interpretation may arise based on the outcome of the judgments made by the officials and who stands to gain from it. The quantity and variety of democratic options in protracted elections have outpaced voters' attention spans and cognitive capacities. These distinguishing characteristics of our voting system contribute to the issues seen in the most recent elections. This paper is mainly based on the 2022 US election."
format: pdf
number-sections: true
bibliography: references.bib
---
